\begin{abstract}

We present \sys, a fully client-side \ac{XSS}
solution, implemented as a Firefox extension. Our approach takes
advantage of available previous knowledge of a web application's
HTML template content, as well as the rich context available in the
DOM to block XSS attacks. \sys prevents \ac{XSS} exploits by using a 
a database of exploit descriptions, which are written with the help of previously recorded
CVEs. CVEs for XSS are widely available and are
one of the main ways to tackle zero-day exploits. \sys effectively
singles out potential injection points for exploits in the HTML and sanitizes content to prevent malicious payloads from appearing in the DOM.

XSnare is a framework for emulating server-side software sanitization on the application client-side. It can protect application users before application developers release patches and before server operators apply them.

We evaluate our approach by studying
104 recent CVEs related to XSS attacks, and find that our tool
defends against 93.75\% of these exploits. To the best of our knowledge,
XSnare is the first rotection mechanism for XSS that is
application-specific, and based on publicly available CVE information.
We show that XSnare's specificity protects users against exploits which evade other, more generic, anti-XSS approaches.

Our performance evaluation shows that our extension's overhead on web page loading time is less than 10\% for 72.6\% of the sites studied.
%
\iv{Can you be more specific/descriptive with 'of the sites studied.' -- like 'of the sites in the Alexa top 500 list.' ?}

\end{abstract}
