\section{Implementation} \label{implementation}

We have implemented our browser extension in Firefox 69.0. Our signatures are currently stored in a local JavaScript file in the extension package. We have decided to implement this tool as an extension due to the following main benefits:
\begin{itemize}
	\item \textbf{Ease of deployment and adoption}. Most modern browsers provide a convenient way to upload extensions to their respective official sites (Firefox Add-Ons in the case of Firefox). This eases deployment for the extension developer, and also eases installation for an user, as they can install the tool within the browser in one click, without having to install additional third-party software. Previous client-side work often applies browser modifications. Most users might not be willing to adopt new browsers, since it might affect usability for them.
	\item \textbf{Privileged execution environment}. The extension's logic can lie in a separate environment from the web application code. This is important for security, as it guarantees that any malicious code in the application can not affect the extension's behaviour. If the extension needs to run code within the application, it can maintain security by installing the code before the application's code runs. A web application, on the other hand, can not achieve this level of security in general, as it can not guarantee that its own code will run before any malicious code.
	\item \textbf{Web application context}. Our solution requires knowledge of the application's context to perform several of its tasks. For example, it's useful to know which tab generated a network request to determine whether the response content is safe or not. The extension naturally retains this context.
	\item \textbf{Ability to interpose at the network level and the web application level}. As it lies within the browser, the extension can run both at the network level, e.g., rewrite an incoming response or outgoing request; and at the web application level, e.g., keeping track of click events, or interpose on the application's JavaScript execution. Other types of solutions often have to choose between one or the other. In particular, Firefox provides the filterResponseData method through the webRequest. This allows the extension's background page to analyse and modify incoming network traffic.
\end{itemize}

\begin{algorithm} 
	\SetAlgoLined
	//global DBSignatures\\
	\SetKwProg{verifyResponse}{procedure \emph{verifyResponse}}{}{end}
	\verifyResponse{(responseString, url)}{
	 loadedProbes = runProbes(responseString, url)\\
	 signaturesToCheck $\leftarrow$ []\\
	 \For{probe in loadedProbes}{
	 	signaturesToCheck.append(DBSignatures[probe])\
 	 }
  	 loadedSignatures $\leftarrow$ []\\
  	 \For{signature in signaturesToCheck} {
  	 	\uIf{responseString and url match signature}{
  	 		loadedSignatures.push(signature)\\
  	 	}
  	 }
     versionInfo $\leftarrow$ loadVersions(url, loadedProbes)\\
     endPoints $\leftarrow$ [] \\
     \For{signature in loadedSignatures} {
     	\uIf{(signature,signature.version) $\in$ versionInfo}{
     		endPoints.push(signature.endPointPairs)\\
     	}
    }
	indices $\leftarrow$ [] \\ 
	\For{endPointPair in endPoints} {
		indices.push(findIndices(responseString, endPointPair))\\
	}
	\uIf{discrepancies exist in indices}{
       	Block page load and return\\
	}
	\For{endPointPair in endPoints} {
		sanitize(responseString,indices)\\
	}
		\caption{Network filter algorithm}
		\label{filter_algorithm}
	}
\end{algorithm}

\subsection{Filtering process} \label{filtering_process}
Algorithm \ref{filter_algorithm} describes our network filtering process. In particular, once a request's response comes in through the network, we process it and sanitize it if necessary. Throughout this subsection, line numbers refer to this algorithm.

\subsubsection{Loading signatures} \label{loading_signatures}
Our detector loads signatures and finds injection points in the document. However, there might be a large number of signatures which don't need to be loaded for a specific website. For example, if several signatures are designed for pages running a WordPress plugin, then the extension need not check any of these for a site which is not running WordPress at all. On the other hand, if a site is running WordPress, we might have to check all signatures meant for WordPress, but not others. Therefore, when loading signatures, we proceed in a manner similar to a decision tree. In line 3, the detector first probes the page to identify the underlying framework (we call this the \textbf{software} in our signature language), which is usually found by hints in the document HTML). These probes are framework-specific, and as such, need to be encoded in some way so that the detector can run them. There are two approaches for this: the detector completely takes care of this, and needs to be maintained for changes in frameworks and future technologies, or, the signature developer additionally specifies a more specialized version detector as part of a probe file. We chose to go with the first option, as this provides a greater ease of use for signature developers. 

In our prototype implementation, hard-coding probes into the detector did not imply a substantial amount of work. However, as more signatures are written and more applications are required to be included, this can become an arduous task. We believe the second option can be desirable and would not be a terrible burden for signature developers: for example, the widely popular network mapping tool Nmap \cite{nMap} uses probes in a similar manner, and these are kept in a modifiable file so that advanced users can have more expressibility. After running these probes, the detector loads signatures for the specific software (e.g. all signatures for Joomla! web sites). In line 4-7, the signatures for the given framework are added for further processing.

In lines 8-12, we filter out the ones that do not apply to the current page by iterating through the list of signatures sequentially. The detector checks whether the identifying information of the signature matches the given HTML string and/or URL.

\subsubsection{Version identification} \label{versioning}
We then apply version identification (lines 13-16). Our objective for versioning is that our signatures don't trigger any false positives on websites running patched software. We found this to be one of the harder aspects of signature loading. In many Content Management Systems (CMS), for example, file names are not updated with the latest versions, or do not include them at all, and thus, this information is often hard to come by from the client-side perspective. In the case of WordPress, the wp-admin/plugins.php subpath contains information about all currently active plugins on the site. Unfortunately, this information is only available to admins of the site. While this might not be the bulk of users, it is, on the other hand, the bulk of disclosed CVEs, as described in Section \ref{viability}.


Furthermore, we believe that even if we load a signature when the application has already been fixed at the server-side, it will often preserve the page's functionality, as many of the CVEs describe XSS which happens as a result of unsanitized input that was not meant to be JavaScript code regardless. Motivated by this observed behaviour, our mechanism follows a series of increasingly accurate but less applicable version identifiers: first, we apply frame-work specific version probes (these are maintained in a similar way to software probes, hard-coded in the detector logic). If these are not successful, the signature language provides functionality for version identification in the HTML through regex. If the signature developer considers version information to be unavailable through the HTML, the version in the signature is left blank and the detector applies the signature patch regardless of version, as we can not be sure the page is running patched software. As long as the database is maintained, signatures will evolve in parallel with the software, and can retain backwards compatibility with past versions. Our tool takes advantage of having perfect knowledge of an exploit's conditions, which reduces the rate of false positives compared to a software-agnostic approach.

 
\subsubsection{Injection point search and sanitization} \label{search_and_sanitization}
Once we have the correct signatures, we find the indices for the endpoints using our top-down, bottom-up scan, and need to check for potential malformations in the injection points, as described in Section \ref{multiple_injections} (lines 19-24). The page load is blocked and a message is returned to the user, or if the signature developer specifies so, sanitization proceeds on the new endpoints. Finally, if all \textbf{endPoint} pairs are in the expected order, we sanitize each injection point (lines 25-27).

While our prototype's signature database is currently encoded entirely in the extension software, we envision that a trusted entity can maintain this database, such as those that currently maintain CVE databases, and will have to be audited so that it is not filled with false signatures and existing ones are not compromised.